The purpose of this section is not an exhaustive review of (convex) optimization but rather to mention
some elementary concepts and terms that will prove useful in the following sections. Foremost a brief
discussion of optimality conditions for constrained problems -- the so called Karush-Kuhn-Tucker (KKT)
conditions -- will be given. Closely linked to those conditions, and in some cases even a perquisite for their
validity, are the constraint qualifications which are subsequently discussed.

    \subsection{Karush-Kuhn-Tucker conditions}
    \label{sec:opt:theory:kkt}
    This formulation of the KKT conditions is adapted from explanations in \cite{Nocedal.2006}.
    Before the conditions ca be stated, some definitions are needed. Considering the most general case of a NLP
    \program{}{
        & \minimize{x} & & f(x) \\
        & \st & & h_i(x) = 0, \; \; i \in \mathset{E} \\
        & & & g_i(x) \leq 0, \; \; i \in \mathset{I}
    }
    where $f(x): \mathbb{R}^n \mapsto \mathbb{R}$ denotes the objective function, $\mathset{E}$ and $\mathset{I}$
    are sets of indices corresponding to equality and inequality constraints respectively. Furthermore are
    the functions $f, g$ and $h$ differentiable and real-valued.

    An active set denotes the union of the set of equality constraints and the inequality constraints
    where $g_i(x) = 0$ holds. Thus we can write for the active set at any feasible point $x$
    \Eq{}{
       \mathset{A}(x) = \mathset{E} \cup \left\{ i \in \mathset{I} | g_i(x) = 0 \right\}.
    }

    For the constrained problem stated above the Lagrangian is defined as
    \Eq{}{
        \mathset{L}(x,\lambda,\mu) := f(x) - \sum_{i \in \mathset{E}} \lambda_i h_i(x) - \sum_{i \in \mathcal{I}} \mu_i g_i(x)
    }

    With that the optimality conditions for constrained optimization can be stated.
    First order or necessary KKT conditions must hold at the optimal point $(x^{\ast}, \lambda^{\ast}, \mu^{\ast})$
    \Eq{}{
        \nabla_x \mathcal{L}(x^{\ast}, \lambda^{\ast}, \mu^{\ast}) & = 0, \\
        h_i(x^{\ast}) & = 0, & \forall i \in \mathset{E} \\
        g_i(x^{\ast}) & \leq 0, & \forall i \in \mathset{I} \\
        \mu_i^{\ast} & \geq 0, & \forall i \in \mathset{I} \\
        \mu_i^{\ast} g_i(x^{\ast})& = 0, & \forall i \in \mathset{I} \\
        \lambda_i^{\ast} h_i(x^{\ast})& = 0, & \forall i \in \mathset{E} \\
    }
    The second order or sufficient KKT conditions can be written as
    \todo{check conditions on lagrange multipliers and active set ....}
    \Eq{}{
        w^T \nabla_{xx} \mathcal{L}(x^{\ast}, \lambda^{\ast}, \mu^{\ast})w & > 0, \quad \forall w \neq 0, \\
        \nabla h_i(x^{\ast})^T w & = 0, \quad \forall i \in \mathset{E}, \\
    }

    \subsection{Constraint qualifications}
    \label{sec:opt:theory:cq}

    Constraint qualifications, can ensure the existence of strictly positive Lagrange
    multipliers, such that the unconstrained equivalent problem can be constructed. In general one is interested
    in the weakest possible perquisite to ensure feasibility \todo{feasibility the right word here?} of the problem.
    There are several constraint qualifications proposed in literature, which are differently hard to fulfil
    and verify. In general a minimum point should satisfy some constraint qualifications or regularity conditions.
    Several more constraint qualifications can be found in literature, but will not be stated here.

    \subsubsection{Slater's constraint qualification (SCQ)}
    Among the most widely used constraint qualifications is Slater's constraint qualification
    \Eq{}{
        \exists \tilde{x}, \forall i \in \mathcal{I} : h_i(\tilde{x}) < 0.
    }
    This qualifications essentially states, that there in fact is a point which will fulfil the constraints.

    \subsubsection{Linear independence constraint qualification (LICQ)}
    Another widely used is called the linear independence constraint qualification. It states,
    given the set of of feasible solutions of the original problem $\mathcal{C} = \{x \in \mathcal{X} \; | \; h_i(x) \leq 0
    \forall i \in \mathcal{I} \}$ and the set of active constraints $\mathcal{A}(\bar{x}) = \{i \in \mathcal{i} \; | \; h_i(\bar{x}) = 0 \}$
    \Eq{}{
        \{ \nabla h_i(\bar{x}) \; | \; i \in \mathcal{A}(\bar{x}) \} \qquad \text{is linearly independent}.
    }

    \subsubsection{Mangasarian-Fromovitz constraint qualification (MFCQ)}
    \Eq{}{
        \exists \tilde{u}, \forall i \in \mathcal{A}(\bar{x}) : \nabla h_i(\bar{x})(\tilde{u}) < 0.
    }



