\chapter{Process economics}
\label{chp:ProcesEconomics}
    Aside from question whether a certain process is capable of producing products according to
    specifications, it needs to be investigated if it does so while meeting economic criteria. The modeling
    of process economics is a powerful tool to estimate project profitability. Knowledge of process economics
    is mostly regarded for three types of decisions
    \regitemize{%
    	\item{Compare design options with regard to profitability.}
    	\item{Economically optimize a given design.}
    	\item{Estimate project profitability}
    }%
    In any case the total cost of a given project as well as the cash flow structure will have to be analyzed to supply
    the decision maker with an accurate estimate of the economic conditions. To do so, adequate measures to compare and
    analyze a project in economic terms need to be implemented.
    
    It is evident that, as the more information about a given process becomes available, any cost can be estimated
    more accurately. During the design phase of a process roughly three different qualities of cost estimation can be identified.
    \regitemize{
    	\item{An estimate before designing the process yields an order of magnitude estimation
    		for supporting market research efforts. (Error $> 30\%$})
    	\item{An estimate in the early design phase based on essential process equipment. (Error $\pm 30\%$})
    	\item{An estimate based on an advanced flowsheet and relevant process parameters. (Error $\pm 20\%$})
    }
    Once detail engineering commences, even more accurate calculations with errors reducing to $\pm 5\%$
    can be undertaken\cite{Peters.2003}. At that point a concrete process option will have to be chosen and
    the investment decision, hence the go-ahead for the project,  will already have to be made. All optimization
    measures within the scope of this thesis will already have concluded at that time.
    
    Within \secref{sec:ProjectCost} first we will take a look at how the total cost of a chemical process might be
    estimated at different design stages. Subsequently in \secref{sec:InvestmentCriteria} some different ways
    of evaluating and comparing investment options will be discussed.

    \section{Evaluation of chemical processes}
    \label{sec:ProjectCost}
    \input{Content/Process_econ_theory}
    
    \section{Investment criteria}
    \label{sec:InvestmentCriteria}
    \input{Content/Process_econ_theory_2}
    
    \section{Economic process model}
    \input{Content/Process_econ_models}

