% Task Description
\thispagestyle{plain}

\begin{center}
	\LARGE
	Diploma Thesis\\
	for\\
	Mr. Robert Pack\\
	\vspace{4ex}

	\vspace{3ex} Task Description
\end{center}

\normalsize

Conceptual process design is a task of major importance within the development of new and the retrofit 
of existing processes. While there has been a lot of research on optimization-based process design such 
approaches are rarely integrated in industrial practise. Up to now simulation software is still the standard 
tool for conceptual design. In order to ease the implementation of optimization-based process design in 
industrial practise, the main goal of this thesis is to facilitate a superstructure-based process optimization 
within the process modelling environment \gproms, which is widely applied in industry. Therefore, firstly a 
superstructure formulation for a distillation column model needs to be implemented. In addition, as initialization 
plays a significant role during simulation and optimization, a robust, automated initialization procedure is an 
essential part of the model development. To finally determine an optimal process design an economic model 
of the process needs to be formulated and a solution strategy together with an adequate optimization 
algorithm need to be determined.

In order to validate the capabilities of the structural optimization approach the design of a cost-optimal cryogenic 
air separation process is chosen as an industrially relevant and complex case study. The process is highly coupled, 
in terms of energy and material streams, as it employs a double effect column along with a coupled side stripper column. 
This gives rise to challenges in terms of simulating and operating the process. Due to these complexities the process 
serves as an excellent example to illustrate the effectiveness of optimization strategies.

In addition to the structural optimization different aspects of process design or control can be coupled to or even 
directly be integrated within the optimization. Among those aspects are potentials for heat integration or the question 
of a suitable control structure. Furthermore several uncertainties arise from unknown process parameters such as changing 
feed conditions, product demands or the development of the market conditions. For all these aspects different methodologies 
have been proposed in the literature, which similar to the structural optimization are not really integrated in industrial 
practice yet.  Most or at least some of the methodologies should therefore also be investigated within this thesis in order 
to identify their potential ease of integration and application in the process modelling environment \gproms to 
simultaneously optimize process and equipment to minimize the total process cost with user defined objective functions.

 \vfill{
\begin{flushright}
	\begin{minipage}[r]{10cm}
		\begin{center}
			\hrule\vspace*{2ex}Prof. Efstratios Pistikopoulos\\
			\vspace{2cm}
			\hrule\vspace*{2ex}Prof. Dr.-Ing. Wolfgang Marquardt\\
			\vspace{1cm}
		\end{center}
	\end{minipage}
\end{flushright}
}

Betreuer der Arbeit: Dipl. Ing. Mirko Skiborowski\\
Tag der Abgabe: 23.01.2013
\todoil{color=AVTLight2Blue}{Add due date}
\clearpage
